---
title: "Getting started with matchpointR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting started with matchpointR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE
)
```

```{r setup}
library(matchpointR)
```

## Overview

`matchpointR` provides a small, consistent family of functions for
scraping [wtatennis.com](https://www.wtatennis.com) into tidy data
frames:

| Function                      | Purpose                                    |
|-------------------------------|--------------------------------------------|
| `wta_player_url()`            | Build canonical player URLs.               |
| `wta_get_player_basics()`     | One-row tibble with bio + images.          |
| `wta_get_player_overview()`   | Singles & Doubles career highlights.       |
| `wta_get_player_matches()`    | One row per match, entire history.         |
| `wta_get_rankings()`          | Current singles / doubles leaderboard.     |
| `wta_get_stats()`             | Stat leaderboards (aces, winners, ...).    |

Every function that talks to the network opens (and closes) its own
headless Chrome session through `chromote`.

## A worked example: Kateřina Siniaková

```{r}
url <- wta_player_url(320301, "katerina-siniakova")

bio <- wta_get_player_basics(url, download_images = FALSE)
bio
```

`download_images = TRUE` (the default) additionally downloads the
headshot and the nationality flag into `magick-image` list-columns — set
it to `FALSE` when you only need the metadata.

### Singles vs Doubles highlights

```{r}
wta_get_player_overview(url)
```

### Full match history

```{r}
matches <- wta_get_player_matches(url)
head(matches)
```

`wta_get_player_matches()` clicks the *Show more* button repeatedly until
no more matches are loaded. Raise `max_clicks` only if you hit the
safety cap on a very long career.

## Tour-wide data

### Live rankings

```{r}
wta_get_rankings("singles", top = 50)
wta_get_rankings("doubles", top = 50)
```

### Statistical leaderboards

```{r}
wta_get_stats("aces", top = 25)
wta_get_stats("first-serve-percentage", top = 25)
```

The `metric` argument maps directly to the path segment at
`https://www.wtatennis.com/stats/<metric>`. Browse the site for the
available slugs.

## Tips

- **Coercion.** All columns are returned as character to stay faithful
  to the rendered page. Cast to numeric/date downstream.
- **Selector drift.** If a function suddenly returns zero rows, the
  site's CSS classes have probably been renamed — open an issue.
- **Rate limiting.** `chromote` hits the site as a real browser; be
  considerate if you are iterating over many players.
